Observed vs. Simulated Year Comparison

### 2023-01-30 03-post-process/output-plots-children/10-noise-term-diags.Rmd
Tiny qresid bug fix
apply() was throwing errors in the case that i_first had only one element; this enables apply to be used regardless

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(observable)/2)
  y_last = (max(y_first) + 1):length(observable)
  i_first = as.character(na.omit(empty_names[y_first]))
  i_last = as.character(na.omit(empty_names[y_last]))
  mn_post_first = apply(qresid_post[,i_first], 1, mean)
  mn_post_last = apply(qresid_post[,i_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

>>>>

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(observable)/2)
  y_last = (max(y_first) + 1):length(observable)
  i_first = as.character(na.omit(empty_names[y_first]))
  i_last = as.character(na.omit(empty_names[y_last]))
  mn_post_first = apply(as.matrix(qresid_post[,i_first]), 1, mean)
  mn_post_last = apply(as.matrix(qresid_post[,i_last]), 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first
